### 2018-05-27 manuscript/visualdesign.tex
abstract done

This work we try to answer a couple of questions:

Problem to solve: 
\begin{itemize}
\item \textit{What flows of people with certain demographic characteristics}: multiple attributes, semantic understanding, loose attribute boundary
\item \textit{What the Urban Dynamics of the Group}: where those people go and how they access the ... in a city. the patterns of behaviour classified by different social characteristics.  Including travel purpose, 
\item \textit{Compare of moving patterns between different groups}: what the similar and difference between groups in their traveling behaviour
\end{itemize}

We derive the design considerations:

\begin{itemize}
\item \textbf{C1: semantic understanding of demographic cahracteristics}: since the concept of groups is vague to define directly quantitativily. The visual design needs to consider how to help end-users to pick desirable ones from the mass. 
\item \textbf{C2: multivariate comparison in the constraint of spatial space}: 
\end{itemize}

>>>>

The system design is task-driven. Before diving into the design of system, we introduce  the couple of tasks the system works for.

\begin{itemize}
\item \textit{Identify the group of people with specific individual characteristics (T1)}: multiple attributes, semantic understanding, loose attribute boundary
\item \textit{Explore the mobility patterns of a group (T2)}: where those people go and how they access the ... in a city. the patterns of behaviour classified by different social characteristics, including travel demands. 
\item \textit{Compare mobility patterns among multiple groups (T3)}: what the similar and difference between groups in their traveling behaviour
\end{itemize}

Based on tasks, we derive the design considerations:

\begin{itemize}
\item \textit{C1: multivarible filter of individual characteristics}: Cross filter...
\textbf{C3: referrable transpotation}: TAZ
\item \textit{C2: intuitive understanding/combination understanding of individual characteristics}: since the concept of groups is vague to define directly quantitativily. The visual design needs to consider how to help end-users to pick desirable ones from the mass. 
\item \textit{C3: conventional travel analysis}: TAZ based
\item \textit{C4: multivariate analysis of mobility patterns in the constraint of spatial space}: the analysis of mobility patterns include multivariables, including the conventional spatial and temporal dimensions, as well as travel demands, frequency, etc.
\item \textit{C5: knowledgable, not too fractional findings}
\item \textit{C6: easy comparison}: 
\end{itemize}
